### 2024-11-26 paper/paper.qmd
Update paper.qmd

---
title: "Exploring the Relationship Between Anime Scores, Popularity, and Favorites"
subtitle: "A Correlation Analysis of Anime Ranking"
author: 
  -Doran Wang
thanks: "Code and data are available at: [https://github.com/Wang20030509/Anime_Rating](https://github.com/Wang20030509/Anime_Rating)."
date: today
date-format: long
abstract: "This repository explores the relationship between anime scores, popularity, and favorites by leveraging data obtained from the MyAnimeList API. The dataset was created by extracting ranking data through the API and transforming it into a comprehensive new dataset. Using this data, I conducted an analysis to investigate how popularity and favorites influence anime scores.The primary hypothesis is that popularity has a stronger impact on anime scores—higher popularity is expected to correlate with higher scores. Additionally, I predict that a higher number of favorites also contributes to an increase in scores. The analysis aims to provide insights into these relationships and quantify their respective influences."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(arrow)
library(knitr)

anime_data <- read_parquet("../data/02-analysis_data/cleaned_data.parquet")
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r fig.pos="h"}
#| label: tbl-clean-data
#| tbl-cap: "Preview of the cleaned Anime Ranking dataset"
#| message: false
#| echo: false

colnames(anime_data) <- c("Score", "Popularity", "Number of users who have this work in list","Ranking")

anime_data[1:5, 1:4] |>
  kable()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-11-27 paper/paper.qmd
Update paper.qmd

@@
 date-format: long
-abstract: "This repository explores the relationship between anime scores, popularity, and favorites by leveraging data obtained from the MyAnimeList API.
+abstract: "This paper explores the relationship between anime scores, popularity, and favorites by leveraging data obtained from the MyAnimeList API.
 The dataset was created by extracting ranking data through the API and transforming it into a comprehensive new dataset.

### 2024-12-03 scripts/00-simulate_data.R
Update data and test scripts Upload the new anime data files

@@ -1,52 +1,44 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Simulates a dataset of Anime rating, include the score, popularity,
+  #and favorites
+# Author: Doran Wang
+# Date: 26 November 2024
+# Contact: doran.wang@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed? Make sure you are in the `anime_rating` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
-set.seed(853)
+set.seed(509)
 
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
-)
+# Number of anime titles
+num_titles <- 100
 
-# Political parties
-parties <- c("Labor", "Liberal", "Greens", "National", "Other")
-
-# Create a dataset by randomly assigning states and parties to divisions
-analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
-  state = sample(
-    states,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.25, 0.25, 0.15, 0.1, 0.1, 0.1, 0.025, 0.025) # Rough state population distribution
-  ),
-  party = sample(
-    parties,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.40, 0.40, 0.05, 0.1, 0.05) # Rough party distribution
+# Generate random anime data
+anime_data <- tibble(
+  # Title
+  title = paste("Anime", 1:num_titles),
+  
+  # Random scores (between 1 and 10, rounded to one decimal place)
+  score = round(runif(num_titles, min = 1, max = 10), 1),
+  
+  # Random number of users who listed the anime (e.g., between 10,000 and 1,000,000)
+  num_list_users = sample(10000:1000000, num_titles, replace = TRUE),
+  
+  # Random number of favorites (e.g., between 100 and 50,000)
[…]

### 2024-12-03 scripts/01-test_simulated_data.R

@@ -1,89 +1,95 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests the structure and validity of the simulated Anime Rating dataset.
+# Author: Doran Wang
+# Date: 26 November 2024
+# Contact: doran.wang@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
   # - The `tidyverse` package must be installed and loaded
   # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed? Make sure you are in the `anime_rating` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
+anime_data <- read_csv("data/00-simulated_data/anime_simulated_data.csv")
 
 # Test if the data was successfully loaded
-if (exists("analysis_data")) {
+if (exists("anime_data")) {
   message("Test Passed: The dataset was successfully loaded.")
 } else {
   stop("Test Failed: The dataset could not be loaded.")
 }
 
-
 #### Test data ####
 
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
+# Check if the dataset has 100 rows
+if (nrow(anime_data) == 100) {
+  message("Test Passed: The dataset has 100 rows.")
 } else {
-  stop("Test Failed: The dataset does not have 151 rows.")
+  stop("Test Failed: The dataset does not have 100 rows.")
 }
 
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
+# Check if the dataset has 7 columns
+if (ncol(anime_data) == 7) {
+  message("Test Passed: The dataset has 7 columns.")
 } else {
-  stop("Test Failed: The dataset does not have 3 columns.")
+  stop("Test Failed: The dataset does not have 7 columns.")
 }
 
-# Check if all values in the 'division' column are unique
-if (n_distinct(analysis_data$division) == nrow(analysis_data)) {
-  message("Test Passed: All values in 'division' are unique.")
+# Check if the 'title' column contains only unique values
[…]

### 2024-12-03 scripts/02-download_data.R

@@ -4,8 +4,14 @@
 # Date: 26 November 2024
 # Contact: doran.wang@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Create an account in MyAnimeList(MAL), then apply the client 
-  #accessing the MAL API.
+# Pre-requisites: 
+  # - Create an account in MyAnimeList(MAL), then apply the client accessing 
+    #the MAL API.
+  # - The `tidyverse` package must be installed and loaded
+  # - The `arrow` package must be installed and loaded
+  # - The `httr` package must be installed and loaded
+  # - The `jsonlite` package must be installed and loaded
+
 # Any other information needed? 
   # For not being disclosed, I set the client ID in .Renviron. Method: 
   # 1. install and load package "usethis". 2. run "edit_r_environ()" in console.
@@ -17,7 +23,6 @@
 #### Workspace setup ####
 library(httr)
 library(jsonlite)
-library(opendatatoronto)
 library(tidyverse)
 library(arrow)
 
@@ -27,7 +32,7 @@ library(arrow)
 # CLIENT_ID <- "YOUR_CLIENT_ID"
 
 # API URL
-url <- "https://api.myanimelist.net/v2/anime/ranking?ranking_type=favorite&limit=50&fields=mean,popularity,num_list_users,rank"
+url <- "https://api.myanimelist.net/v2/anime/ranking?ranking_type=favorite&limit=50&fields=title,mean,popularity,num_list_users,rank,num_scoring_users"
 
 # Make the GET request
 response <- GET(
@@ -55,6 +60,7 @@ anime_data <- anime_data$data$node
 
 
 #### Save data ####
-write_parquet(anime_data, "data/01-raw_data/anime_data.parquet") 
+write_parquet(anime_data, "data/01-raw_data/anime_data.parquet")
+
 
          

### 2024-12-03 scripts/03-clean_data.R

@@ -1,11 +1,14 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the raw data
+# Author: Doran Wang
+# Date: 26 November 2024
+# Contact: doran.wang@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+  # - Access the 02-download_data.R first
+  # - The `tidyverse` package must be installed and loaded
+  # - The `arrow` package must be installed and loaded
+# Any other information needed? install the package `arrow`
 
 #### Workspace setup ####
 library(tidyverse)
@@ -14,10 +17,18 @@ library(arrow)
 #### Clean data ####
 raw_data <- read_parquet("../Anime_Rating/data/01-raw_data/anime_data.parquet")
 
+num_favorites <- c(230821,229949,215928, 192667, 176851, 176089, 114513, 110665,
+                   109387, 92800, 92031, 91959, 90265, 86868, 84622, 81500, 79930,
+                   77161, 76525, 75221, 70931, 69642, 69027, 65103, 63768, 59973,
+                   59777, 57613, 57185, 56722, 55,665, 53748, 52657, 50904,50454,
+                   50242, 49712, 49147, 49088, 48928, 48026, 47912, 47841, 46890,
+                   46067, 45355, 40702, 40448, 39821, 39658)
 cleaned_data <-
   raw_data |>
   janitor::clean_names() |>
-  select(mean, popularity, num_list_users, rank) |>
+  select(title,mean,rank, popularity, num_list_users,num_scoring_users) |>
+  mutate(num_favorites = num_favorites[1:nrow(cleaned_data)], 
+          rank_favorites = seq_along(title)) |>
   rename(score = mean
          ) |> 
   tidyr::drop_na()

### 2024-12-03 scripts/04-test_analysis_data.R

@@ -10,60 +10,93 @@
 
 #### Workspace setup ####
 library(tidyverse)
-library(testthat)
+library(arrow)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
+# Load the cleaned data
+cleaned_data <- read_parquet("data/02-analysis_data/cleaned_data.parquet")
 
+# Test if the data was successfully loaded
+if (exists("cleaned_data")) {
+  message("Test Passed: The dataset was successfully loaded.")
+} else {
+  stop("Test Failed: The dataset could not be loaded.")
+}
 
 #### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
-})
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
-})
+# Check if the dataset has the correct number of rows (replace 50 with actual row count if known)
+expected_rows <- 50  # Update this based on your expectations
+if (nrow(cleaned_data) == expected_rows) {
+  message("Test Passed: The dataset has ", expected_rows, " rows.")
+} else {
+  stop("Test Failed: The dataset does not have ", expected_rows, " rows.")
+}
 
-# Test that the 'division' column is character type
-test_that("'division' is character", {
-  expect_type(analysis_data$division, "character")
-})
+# Check if the dataset has the expected number of columns (replace 8 with actual column count if known)
+expected_columns <- 8  # Update this based on your expectations
+if (ncol(cleaned_data) == expected_columns) {
+  message("Test Passed: The dataset has ", expected_columns, " columns.")
+} else {
+  stop("Test Failed: The dataset does not have ", expected_columns, " columns.")
+}
 
-# Test that the 'party' column is character type
-test_that("'party' is character", {
-  expect_type(analysis_data$party, "character")
-})
+# Check if all values in specific columns are unique (e.g., "title")
+if (n_distinct(cleaned_data$title) == nrow(cleaned_data)) {
+  message("Test Passed: All values in 'title' are unique.")
+} else {
+  stop("Test Failed: The 'title' column contains duplicate values.")
+}
 
-# Test that the 'state' column is character type
-test_that("'state' is character", {
-  expect_type(analysis_data$state, "character")
-})
+# Check if numeric columns have valid ranges (e.g., "score" is between 1 and 10)
[…]

### 2024-12-03 scripts/04-test_analysis_data.R
Update the project
fill the missing info and change the Rproj name

@@ -1,11 +1,13 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the structure and validity of the cleaned Anime Rating dataset.
+# Author: Doran Wang
+# Date: 26 November 2024
+# Contact: doran.wang@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites:
+  # - The `tidyverse` and `arrow` packages must be installed and loaded
+  # - 03-simulate_data.R must have been run
+# Any other information needed? Make sure you are in the `anime_rating` rproj
 
 
 #### Workspace setup ####

### 2024-12-03 other/datasheet/datasheet.qmd
Update datasheet

---
title: "Datasheet for 'MyAnimeList[@myanimelist] Dataset'"
subtitle: "Dataset for anime analytics"
author: 
  - Doran Wang
thanks: "Code and data are available at: [https://github.com/Wang20030509/Anime_Rating](https://github.com/Wang20030509/Anime_Rating)."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This dataset is a collection of data from MyAnimeList[@myanimelist], including manually compiled 'num_favorites' data, intended for analysis of anime popularity and user preferences."
format: pdf
number-sections: true
bibliography: references_datasheet.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable analysis of anime and user preferences from MyAnimeList[@myanimelist]. Specifically, the gap addressed was the unavailability of "num_favorites" data through the API, which was manually collected to enhance the dataset.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - Doran Wang created the dataset.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The dataset creation was self-funded.
4. *Any other comments?*
    - The dataset combines automated API data and manually collected information to ensure completeness.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Each instance represents an anime entry from MyAnimeList[@myanimelist], including details like title, genre, rating, and the manually added number of favorites.
2. *How many instances are there in total (of each type, if appropriate)?*
	- 50 obs (I set the limit, it can be more).
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset is a subset of all anime entries on MyAnimeList[@myanimelist], focusing on a curated selection relevant for analysis.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance includes features such as title, score, genre, and num_favorites (manually collected).
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- No specific label or target was defined; the dataset is for exploratory analysis and modeling.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- Some attributes, like character details or specific user interactions, are not included because they are not available via the API.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- No explicit relationships are included.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- Splits can be created based on user-defined analysis needs, such as genre or rating distribution.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- Manual entry of "num_favorites" may introduce small human errors despite best efforts for accuracy.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset relies on  MyAnimeList[@myanimelist] (MAL) as the source. Since MAL is a live platform, changes to its structure may affect reproducibility.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was directly observable through the use of the MyAnimeList API[@malAPI]. Information about anime titles, ratings, popularity, number of users, and other metrics were directly extracted via automated requests to the API
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Data was collected through the MyAnimeList API [@malAPI], which provides detailed information on anime, including ratings, popularity, and other related metadata. 
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- I sampled popular anime titles, I use a probabilistic sampling strategy based on user ratings or popularity
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Student: Doran Wang 
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- Data was collected over November 2024. The dataset reflects the current state of information as of the last API query on November 30, 2024.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- The dataset was collected using publicly available API data from MyAnimeList[@myanimelist], which does not involve personal information or sensitive data. As such, no formal ethical review was required. However, the dataset complies with the terms of use provided by the MyAnimeList[@myanimelist] platform.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was obtained from a third-party source, specifically the MyAnimeList API. The dataset does not involve collecting personal data from individuals directly.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- As the data was collected from the MyAnimeList[@myanimelist] platform, which is publicly available and adheres to the site's terms and conditions, individual notifications were not required. The platform’s terms of use govern the collection of data through the API.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- The dataset does not involve direct data collection from individuals, as it relies on publicly available information from MyAnimeList[@myanimelist]'s platform. MyAnimeList[@myanimelist] users consented to the use of their data through their agreement to the platform's terms of service, which govern the use of publicly available data.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- Since the dataset does not involve the direct collection of personal data from individuals, there was no mechanism for individuals to revoke their consent.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No data protection impact analysis was required, as the data does not involve personally identifiable information or sensitive data.
12. *Any other comments?*
	- The dataset complies with MyAnimeList’s API terms of service, and no personal information is included in the dataset. It is intended for use in analysis of anime-related trends and statistics, without any personal data related to the users of MyAnimeList[@myanimelist].

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Not
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- None
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- None
4. *Any other comments?*
	- None

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- The dataset has been used for personal analysis related to anime ratings, popularity, and trends. The analysis includes exploring the relationship between user ratings and various attributes such as genre, score, and ranking.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- The dataset is used for personal projects and is hosted on GitHub. You can access all project content at https://github.com/Wang20030509/Anime_Rating.
3. *What (other) tasks could the dataset be used for?*
	- The dataset could be used for sentiment analysis of anime ratings, recommendation systems based on user preferences, analyzing trends in anime genres, or exploring how popularity correlates with ratings. Additionally, it could be used for modeling user behavior or predicting anime success.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- The dataset contains only publicly available data from the MyAnimeList API, which does not include any personally identifiable information. However, users of the dataset should be aware that the dataset could reflect certain biases inherent in the MyAnimeList[@myanimelist] community, such as demographic skew (e.g., age or location of users). This could influence the generalizability of any analysis. To mitigate this, users should consider supplementing this data with more diverse sources or applying fairness-aware techniques when analyzing user behavior.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- The dataset should not be used for any task that involves personal data analysis or attempts to infer sensitive personal characteristics, as it does not contain such data. It should also not be used to make assumptions about the broader population of anime viewers, as the dataset may not be representative of all global anime fans.
6. *Any other comments?*
	- The dataset is regularly updated with new data from MyAnimeList[@myanimelist] to ensure its relevance and accuracy for ongoing analysis.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- The dataset will be made publicly available on GitHub, and it may be used by third parties for various research or personal analysis purposes. No specific third-party entities are involved in the distribution at this time.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset will be distributed via a GitHub repository, where users can download the data directly. It does not have a DOI at this time.
3. *When will the dataset be distributed?*
	- The dataset is already available for public access on GitHub at https://github.com/Wang20030509/Anime_Rating, and will continue to be updated as new data is collected.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset will be distributed under a permissive open-source license, such as the MIT License, which allows anyone to use, modify, and distribute the dataset, with the condition that proper attribution is given. A link to the license will be provided in the GitHub repository.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- The dataset is based on publicly available data from the MyAnimeList API, which may have its own terms of use. Users should review the MyAnimeList[@myanimelist] Terms of Service before using the data.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- There are no known export controls or regulatory restrictions that apply to the dataset at this time.
7. *Any other comments?*
	- The dataset will be maintained and updated periodically to reflect new data available via the MyAnimeList API. Users are encouraged to check the GitHub repository for the latest versions.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The dataset will be maintained by Doran Wang, the author of the GitHub repository.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The dataset owner can be contacted via email at doran.wang@mail.utoronto.ca.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- There is no erratum at the moment, but any necessary corrections will be updated in the GitHub repository.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- The dataset will be updated regularly based on new data from the MyAnimeList API. Updates will be made as the API provides new information. Updates will be communicated via the GitHub repository, with details in the commit logs.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- The dataset does not contain personal data, so retention and deletion limits do not apply.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions of the dataset may not be maintained; however, users can access the commit history on GitHub to retrieve past versions if needed.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- Contributions can be made via pull requests on the GitHub repository. All contributions will be reviewed and validated by the dataset owner before being merged. Any accepted contributions will be communicated via the repository’s commit logs.
8. *Any other comments?*
	- No further comments at this time.

\newpage

# References

### 2024-12-04 other/datasheet/datasheet.qmd
Update Paper

@@
 thanks: "Code and data are available at: [https://github.com/Wang20030509/Anime_Rating](https://github.com/Wang20030509/Anime_Rating)."
-date: "`r Sys.time()`"
-date-format: "D MMMM YYYY"
+date: today
+date-format: long
 abstract: "This dataset is a collection of data from MyAnimeList[@myanimelist], including manually compiled 'num_favorites' data, intended for analysis of anime popularity and user preferences."

### 2024-12-04 paper/paper.qmd
Update Paper

@@
 format: pdf
+toc: true
 number-sections: true
@@
 
+raw_data <- read_parquet("../data/01-raw_data/anime_data.parquet")
 anime_data <- read_parquet("../data/02-analysis_data/cleaned_data.parquet")
@@
 
-Overview paragraph
+Anime has evolved from a niche entertainment medium to a global cultural phenomenon, with millions of viewers and dedicated fan communities around the world.
+As part of this growth, platforms like MyAnimeList [@myanimelist] have become key hubs for anime enthusiasts to rate, review, and interact with anime content.
+These platforms generate vast amounts of data that can provide insights into user preferences and trends in anime reception.
+MyAnimeList, in particular, offers detailed metadata for thousands of anime titles, including user-generated ratings, popularity scores, and other key metrics such as the number of favorites.
+This paper leverages data from the MyAnimeList API [@malAPI] to explore the relationships between anime scores, popularity, and favorites.
 
-Estimand paragraph
+The central estimand of this study is the relationship between the popularity and number of favorites of an anime and its score, as recorded on MyAnimeList.
+Specifically, this research seeks to quantify how these factors—popularity and favorites—affect the overall score of an anime title.
+We hypothesize that higher popularity and a larger number of favorites will be positively correlated with higher scores.
+This analysis aims to provide a clearer understanding of the magnitude and direction of these effects, offering insights into what drives anime success on community-driven platforms.
 
-Results paragraph
+The analysis confirms that there is a significant positive relationship between both popularity and the number of favorites with anime scores.
+Popularity, measured by the number of users who rated an anime, is found to have a particularly strong influence on scores, supporting the hypothesis that more popular anime tend to receive higher ratings.
+Similarly, the number of favorites is positively associated with scores, indicating that anime with greater fan engagement tend to receive better ratings.
+These findings highlight the importance of community interaction and popularity in determining the perceived quality of anime.
 
-Why it matters paragraph
+Understanding the factors that influence anime ratings is crucial for several reasons.
+For anime creators and studios, it can provide insights into audience preferences, guiding future production and marketing strategies.
+For platform developers, such as MyAnimeList, it helps improve user experience by understanding how to foster engagement and enhance the visibility of popular titles.
+Additionally, this research contributes to the broader field of data-driven analysis in entertainment media, providing a model for evaluating user engagement in other areas of digital content.
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+The remainder of this paper is structured as follows: @sec-data provides an overview of the dataset, describing the data collected from the MyAnimeList API [@malAPI].
+@sec-model presents the modeling approach, which includes correlation analysis and linear regression to assess the relationships between the variables.
+@sec-result presents the analysis results, followed by a discussion of the implications and limitations in @sec-discussion.
 
@@
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+For this analysis, the dataset was compiled using data extracted from the MyAnimeList API, which provides key variables such as anime titles, scores, popularity, and the number of list users.
+The "number of favorites" data, however, was not available through the API, so it was manually compiled by directly listing the values from the MyAnimeList website and included in the dataset for analysis.
+These data points were then cleaned and processed for analysis using the statistical programming software R [@citeR].
+The analysis utilized several R packages from the tidyverse [@citeTidyverse], including dplyr [@citeDplyr] for data wrangling, ggplot2 [@citeGgplot] for visualization and ``knitr` [@citeKnitr]`.
+Data processing tasks, such as handling missing values and transforming variables, were carried out to ensure the dataset was ready for analysis.
 
-Overview text
+The dataset contains observations for hundreds of anime titles, each accompanied by their respective attributes.
+The data was collected from a variety of genres, years, and user ratings, ensuring a comprehensive snapshot of anime as rated by MyAnimeList users.
+Following the methodology described in @tellingstories, we consider the correlation between popularity, favorites, and scores to explore the factors that influence anime ratings.
 
@@
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+The dataset used in this study was compiled from the MyAnimeList API, which provides a variety of metrics related to anime titles.
+The data collection spans a broad range of anime, including series from different genres, release years, and popularity levels.
+Each entry in the dataset represents a unique anime title, and the associated variables include score, popularity, number of list users, and number of favorites, among others.
 
-## Outcome variables
+To measure popularity, the popularity score is derived from the total number of users who have rated or added the anime to their lists on MyAnimeList.
+This variable provides a rough indication of how well-known or widely watched a particular anime is within the community.
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
+The score variable is an average rating based on user feedback, with each user rating an anime on a scale from 1 to 10.
+The score reflects the collective opinion of MyAnimeList users and is a key metric for understanding the general reception of an anime.
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+The number of favorites, which was not provided directly by the API, was manually compiled by listing the number of favorites for each anime directly from the MyAnimeList website.
+This variable reflects how many users have specifically marked an anime as a "favorite," which can be interpreted as a more personal, long-term engagement with the title.
+Since it was manually compiled, the accuracy of this data depends on the consistency of the manual entries across titles.
 
-```{r fig.pos="h"}
-#| label: tbl-clean-data
-#| tbl-cap: "Preview of the cleaned Anime Ranking dataset"
+To ensure consistency and reliability, all metrics were extracted using the MyAnimeList API’s standardized definitions, and the dataset was processed and cleaned using R [@citeR] and the tidyverse [@citeTidyverse] packages.
+Missing data were handled appropriately, with rows containing missing values being excluded from the analysis.
+
+This dataset allows us to explore how factors like popularity and favorites influence anime scores.
+By correlating these variables, we aim to better understand the elements that contribute to higher ratings and broader appeal among the anime community.
+However, it is important to note that there are some limitations to these measurements.
+The popularity and score data are based solely on MyAnimeList users, and therefore may not fully represent the global anime audience.
+Additionally, the manual compilation of the number of favorites introduces a potential source of human error, though efforts were made to ensure accuracy.
+
+These variables, combined with the rich data provided by the MyAnimeList API, enable an in-depth analysis of anime ratings, offering valuable insights into the factors that influence the perception of anime quality in the community.
+
+## Raw Data
+The raw dataset, which shows in @tbl-raw-anime-scores in Appendix @sec-data-details, used in this study was sourced from the MyAnimeList API and contains several important variables, as shown in the below.
+The dataset includes 200 anime titles, each represented by the following columns:
+
+ - id: A unique identifier for each anime title in the dataset.
+ - title: The name of the anime.
+ - mean: The average score given by users, ranging from 1 to 10.
+ - popularity: The rank of the anime based on the number of users who have added the anime to their list. (1 means the highest)
+ - num_list_users: The number of users who have added the anime to their list (either for watching, completed, etc.).
+ - rank: The rank of the anime based on its popularity among other titles.
+ - num_scoring_users: The number of users who have rated the anime.
+
+## Cleaned
+
+```{r}
+#| label: tbl-anime-scores
+#| tbl-cap: "Preview of the anime scores dataset"
 #| message: false
@@
 
-colnames(anime_data) <- c("Score", "Popularity", "Number of users who have this work in list","Ranking")
+colnames(anime_data) <- c("Title", "Score", "rank", "Popularity", "Number of List Users","Number of Scoring Users", "Number of Favorites" , "Most Favorited")
 
-anime_data[1:5, 1:4] |>
+anime_data[1:5, 1:7] |>
   kable()
+
 ```
 
-Talk more about it.
+The cleaned dataset shows in @tbl-anime-scores, used in this study builds upon the raw data extracted from the MyAnimeList API.
+In addition to the original variables—such as score, popularity, number of list users, rank, and number of scoring users—two new columns were created to enhance the analysis: rank_favorites and num_favorites.
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+ - rank_favorites: This new variable was created by sorting the anime titles according to the number of favorites.
+The rank is based on the order of the number of favorites, allowing for a more specific understanding of anime popularity from a fan engagement perspective.
+It essentially ranks the anime based on how much attention and affection it has garnered from the community in terms of user engagement with the "favorite" feature.
+
+ - num_favorites: The number of favorites is another newly added variable that was not available in the original MyAnimeList API data.
+This data was manually compiled by directly listing the number of favorites for each anime from the MyAnimeList website.
+This manual entry was necessary as the API did not provide this metric, and it offers insight into user preferences and long-term engagement with anime titles.
+
+After these new columns were added, the dataset was cleaned and processed to remove missing or irrelevant values, ensuring that only the most complete and relevant data were used for analysis.
+The cleaned dataset now provides a comprehensive view of how popularity, favorites, and scores interact to influence the ratings and reception of anime titles.
+
+## Data Visualization
+The outcome variable in this analysis is the anime score, which is a critical metric for understanding the general reception of an anime by the MyAnimeList community.
+The anime score is an average rating given by users of MyAnimeList on a scale from 1 to 10.
+It reflects the collective opinion of the community and is often used as a benchmark for the quality and popularity of anime titles.
+
+### Popularity
 
 ```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
+#| label: fig-popularity
+#| fig-cap: "Relationship between popularity and anime scores"
 #| echo: false
@@
 
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
+ggplot(anime_data, aes(x = `Number of List Users`, y = Score)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = "blue") +
+  labs(title = "Anime Popularity vs. Score", x = "Number of List Users ", y = "Score")
 
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
 ```
+The popularity variable is a key predictor that measures how widely known an anime is, as indicated by the number of users who have rated it.
+The higher the popularity score, the more likely it is that the anime has a larger audience, which we expect will correlate with a higher score.
+Similarly, number of favorites reflects the level of long-term engagement with an anime.
+Users who favorite an anime are signaling a deeper personal attachment or preference for it, and this engagement is expected to positively influence its score.
 
-Talk way more about it.
+### Favorites
+```{r}
+#| label: fig-favorites
+#| fig-cap: "Effect of number of favorites on anime scores"
+#| echo: false
+#| warning: false
+#| message: false
 
-## Predictor variables
+ggplot(anime_data, aes(x = `Number of Favorites`, y = Score)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = "red") +
+  labs(title = "Number of Favorites vs. Anime Score", x = "Number of Favorites", y = "Score")
 
-Add graphs, tables and text.
+```
+We also consider the ranking of anime, which is another important aspect influencing its visibility and perceived quality.
+Higher-ranked anime typically have higher scores, as they are often more popular or well-received by the community.
 
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+These outcome variables—anime score, popularity, and number of favorites—are central to this analysis.
+By examining how these variables interact, we aim to gain a deeper understanding of the dynamics between anime ratings and community engagement.
 
-# Model
+# Model {#sec-model}
 
-The goal of our modelling strategy is twofold. Firstly,...
+The goal of our modeling strategy is twofold.
+Firstly, we aim to explore the relationship between the anime score (the dependent variable) and key predictors such as popularity and number of favorites (the independent variables).
+Secondly, we seek to quantify how these variables contribute to predicting the anime score using a linear regression model and, if necessary, a Bayesian framework to account for uncertainty and prior beliefs.
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+Here, we briefly describe the linear regression model used to investigate how popularity and number of favorites influence anime scores.
+Additional background details and diagnostics are included in [Appendix - @sec-model-details].
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+Define $y_i$ as the anime score for anime $i$, which represents the average rating given by users on MyAnimeList.
+Let $x_{i1}$ be popularity and $x_{i2}$ be the number of favorites for the anime.
+The model assumes that the anime score is linearly related to these predictors.
 
@@
 y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
+\mu_i &= \alpha + \beta_1 \times \mbox{popularity}_i + \beta_2 \times \mbox{favorites}_i \\
 \alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
+\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
 \sigma &\sim \mbox{Exponential}(1)
@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+Where:
+$y_i$ is the anime score for anime $i$,
+$\mu_i$ is the expected score for anime $i$ based on the predictors,
+popularity is the number of users who have the anime in their list,
+favorites is the manually compiled number of favorites for the anime,
+$\alpha$ is the intercept term,
+$\beta_1$ and $\beta_2$ are the regression coefficients for popularity and number of favorites,
+$\sigma$ is the standard deviation of the residuals (i.e., the model error).
+We run the model in R [@citeR] using the rstanarm package from @rstanarm.
+The priors are chosen to be non-informative, with default values based on the assumption that we have little prior knowledge about the relationships between the variables
 
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+We expect a positive relationship between popularity and anime score.
+Specifically, we hypothesize that more popular anime, which have a higher number of ratings, are likely to receive higher average scores.
+Similarly, we expect that a higher number of favorites will also lead to higher anime scores, reflecting stronger fan engagement with the title.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+By using this model, we aim to quantify the strength of these relationships and gain insights into the factors that contribute to a title’s success in terms of user ratings on MyAnimeList.
 
-# Results
+# Results {#sec-result}
 
@@
 
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
 ```
@@
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
 ```
 
-# Discussion
+# Discussion {#sec-discussion}
 
@@
 
-# Additional data details
+# Additional data details {#sec-data-details}
+
+```{r}
+#| label: tbl-raw-anime-scores
+#| tbl-cap: "The Raw Dataset of the anime scores dataset (only first 5 rows)"
+#| message: false
+#| warning: false
+#| echo: false
+
+raw_data[1:5, 1:3]|>
+  kable()
+
+raw_data[1:5, 4:ncol(raw_data)]|>
+  kable()
+```
+
+Here is how the score(mean) calculated:
+All scores given in the database are calculated as a weighted score.
+
+Weighted Score = $(v / (v + m)) * S + (m / (v + m)) * C$
+
+$S$ = Average score for the anime/manga
+$v$ = Number users giving a score for the anime/manga †
+$m$ = Minimum number of scored users required to get a calculated score
+$C$ = The mean score across the entire Anime/Manga database
+
+† Note that v does not correspond to the "number of scored users" as seen on the database page.
+Scores from users who have not viewed 1/5 of the series upon its completion are not included.
+Scores given from illegitimate accounts created to sway votes are also not included in the scoring algorithm.
+
+Not Yet Aired entries have no score and will display N/A. Entries that do not meet the minimum number of scored users will also not display a calculated score.
+
+Top Anime/Manga Rankings
+The "Top Upcoming" and "Most Popular" rankings are ordered by the number of users who have added the entry to their list.
+All other Top Anime and Top Manga rankings are ordered by weighted score, as calculated above.
+Please note that while R18+ entries calculate a weighted score, they are excluded from the rankings.
+Music Videos are also excluded from Top Anime.
 
@@
 
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
 ```
@@
 
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
 ```

### 2024-12-04 scripts/02-download_data.R

@@ -32,7 +32,7 @@ library(arrow)
 # CLIENT_ID <- "YOUR_CLIENT_ID"
 
 # API URL
-url <- "https://api.myanimelist.net/v2/anime/ranking?ranking_type=favorite&limit=50&fields=title,mean,popularity,num_list_users,rank,num_scoring_users"
+url <- "https://api.myanimelist.net/v2/anime/ranking?ranking_type=favorite&limit=200&fields=title,mean,popularity,num_list_users,rank,num_scoring_users"
 
 # Make the GET request
 response <- GET(

### 2024-12-04 scripts/03-clean_data.R

@@ -17,6 +17,9 @@ library(arrow)
 #### Clean data ####
 raw_data <- read_parquet("../Anime_Rating/data/01-raw_data/anime_data.parquet")
 
+raw_data <- raw_data %>%
+  slice_head(n = 50)
+
 num_favorites <- c(230821,229949,215928, 192667, 176851, 176089, 114513, 110665,
                    109387, 92800, 92031, 91959, 90265, 86868, 84622, 81500, 79930,
                    77161, 76525, 75221, 70931, 69642, 69027, 65103, 63768, 59973,

### 2024-12-04 paper/paper.qmd
Update Paper

@@
 library(knitr)
+library(rstanarm)
+library(modelsummary)
 
@@
 anime_data <- read_parquet("../data/02-analysis_data/cleaned_data.parquet")
+cleaned_data <- read_parquet("../data/02-analysis_data/cleaned_data.parquet")
+anime_model <- readRDS(file = here::here("models/anime_model.rds"))
 ```
@@
 These data points were then cleaned and processed for analysis using the statistical programming software R [@citeR].
-The analysis utilized several R packages from the tidyverse [@citeTidyverse], including dplyr [@citeDplyr] for data wrangling, ggplot2 [@citeGgplot] for visualization and ``knitr` [@citeKnitr]`.
+The analysis utilized several R packages from the tidyverse [@citeTidyverse], ggplot2 [@citeGgplot] for visualization, `rstanarm` [@rstanarm], `arrow` [@citearrow] and `knitr` [@citeKnitr]`.
 Data processing tasks, such as handling missing values and transforming variables, were carried out to ensure the dataset was ready for analysis.
@@
 ```{r}
-#| label: fig-popularity
-#| fig-cap: "Relationship between popularity and anime scores"
+#| label: fig-favorites-histogram
+#| fig-cap: "Histogram of Popularity for Top 10 Highest-Rated Anime"
 #| echo: false
@@
 
-ggplot(anime_data, aes(x = `Number of List Users`, y = Score)) +
-  geom_point() +
-  geom_smooth(method = "lm", se = FALSE, color = "blue") +
-  labs(title = "Anime Popularity vs. Score", x = "Number of List Users ", y = "Score")
+# Select top 10 highest rated anime based on the Score
+top_10_anime <- cleaned_data %>%
+  arrange(desc(score)) %>%
+  head(10)
 
+# Create a histogram of Number of Favorites with different colors for each anime title
+ggplot(top_10_anime, aes(x = score, y = num_list_users, fill = title)) +
+  geom_bar(stat = "identity") +
+  labs(
+    x = "Score",
+    y = "Number of Users who Have Anime in List"
+  ) +
+  scale_fill_manual(values = RColorBrewer::brewer.pal(10, "Set3")) +  # Color palette for different titles
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
+    axis.title = element_text(size = 12, face = "bold"),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_text(size = 10),
+    legend.title = element_text(size = 12),
+    legend.text = element_text(size = 10)
+  ) +
+  guides(fill = guide_legend(title = "Anime Title"))  # Add legend for titles
 ```
@@
 ```{r}
-#| label: fig-favorites
-#| fig-cap: "Effect of number of favorites on anime scores"
+#| label: fig-favorites-histogram
+#| fig-cap: "Histogram of Number of Favorites for Top 10 Highest-Rated Anime"
 #| echo: false
@@
 
-ggplot(anime_data, aes(x = `Number of Favorites`, y = Score)) +
-  geom_point() +
-  geom_smooth(method = "lm", se = FALSE, color = "red") +
-  labs(title = "Number of Favorites vs. Anime Score", x = "Number of Favorites", y = "Score")
+# Select top 10 highest rated anime based on the Score
+top_10_anime <- cleaned_data %>%
+  arrange(desc(score)) %>%
+  head(10)
 
+# Create a histogram of Number of Favorites with different colors for each anime title
+ggplot(top_10_anime, aes(x = score, y = num_favorites, fill = title)) +
+  geom_bar(stat = "identity") +
+  labs(
+    title = "Histogram of Number of Favorites for Top 10 Highest-Rated Anime",
+    x = "Score",
+    y = "Number of Favorites"
+  ) +
+  scale_fill_manual(values = RColorBrewer::brewer.pal(10, "Set3")) +  # Color palette for different titles
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
+    axis.title = element_text(size = 12, face = "bold"),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_text(size = 10),
+    legend.title = element_text(size = 12),
+    legend.text = element_text(size = 10)
+  ) +
+  guides(fill = guide_legend(title = "Anime Title"))  # Add legend for titles
 ```
@@
 Where:
-$y_i$ is the anime score for anime $i$,
-$\mu_i$ is the expected score for anime $i$ based on the predictors,
-popularity is the number of users who have the anime in their list,
-favorites is the manually compiled number of favorites for the anime,
-$\alpha$ is the intercept term,
-$\beta_1$ and $\beta_2$ are the regression coefficients for popularity and number of favorites,
-$\sigma$ is the standard deviation of the residuals (i.e., the model error).
+ - $y_i$ is the anime score for anime $i$,
+ - $\mu_i$ is the expected score for anime $i$ based on the predictors,
+ - popularity is the number of users who have the anime in their list,
+ - favorites is the manually compiled number of favorites for the anime,
+ - $\alpha$ is the intercept term,
+ - $\beta_1$ and $\beta_2$ are the regression coefficients for popularity and number of favorites,
+ - $\sigma$ is the standard deviation of the residuals (i.e., the model error).
 We run the model in R [@citeR] using the rstanarm package from @rstanarm.
@@
 Our results are summarized in @tbl-modelresults.
+The Bayesian model used in this analysis provides insights into how popularity and number of favorites influence anime scores.
+The model confirms some expected patterns and reveals counter-intuitive findings.
+
+## Popularity vs. Anime Score
+The relationship between popularity and anime score was initially expected to show a clear positive correlation.
+However, our model suggests that the popularity of an anime (measured by the number of users who have rated it) does not consistently lead to higher anime scores.
+In fact, some anime with very high scores are ranked low in popularity, while others with high popularity have lower scores.
+This result is counter-intuitive, as we might expect that more popular anime would receive higher ratings.
+```{r}
+#| label: fig-popularity-vs-score
+#| fig-cap: "Relationship between popularity and anime scores"
+#| echo: false
+#| warning: false
+#| message: false
+
+ggplot(cleaned_data, aes(x = popularity, y = score)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = "blue") +
+  labs(title = "Popularity vs Anime Score", x = "Popularity", y = "Anime Score")
+
+```
+
+The plot @fig-popularity-vs-score illustrates this weak relationship.
+Despite high popularity indicating more user involvement, it does not guarantee higher anime scores.
+This suggests that while popularity can reflect a broad audience, it does not necessarily indicate high quality or fan approval.
+
+## Number of Favorites vs. Anime Score
+
+On the other hand, number of favorites consistently shows a positive relationship with anime scores.
+Anime that are favored by more users tend to receive higher ratings, confirming our hypothesis that favorites is a more reliable indicator of an anime’s quality and fan engagement than popularity.
+
+```{r}
+#| label: fig-favorites-vs-score
+#| fig-cap: "Relationship between number of favorites and anime scores"
+#| echo: false
+#| warning: false
+#| message: false
+
+ggplot(cleaned_data, aes(x = num_favorites, y = score)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = "red") +
+  labs(title = "Number of Favorites vs Anime Score", x = "Number of Favorites", y = "Anime Score")
+
+```
+In @fig-favorites-vs-score, we observe a clear positive trend: as the number of favorites increases, so does the anime score.
+This relationship suggests that user engagement, specifically through favorites, is a strong predictor of how highly an anime is rated by the community.
+
+## Summary of Results
+To summarize, our analysis reveals two key findings:
+
+Popularity and anime score show a weak relationship.
+While we might expect more popular anime to score higher, this is not consistently true.
+Some anime with high scores have relatively low popularity rankings, and vice versa.
+Number of favorites is a much stronger predictor of anime scores, showing a clear and consistent positive relationship.
+This suggests that deeper engagement (i.e., when users favorite anime) is a better indicator of the anime’s perceived quality.
 
@@
 #| message: false
+#| label: tbl-modelresults
 
-library(rstanarm)
-
+modelsummary(
+  list(
+    "Anime Score" = anime_model
+  ),
+  statistic = "mad"
+  )
 ```
 
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-```
+The table @tbl-modelresults presents the summary of the correlation coefficients and p-values for the relationships between popularity, number of favorites, and anime score.
+As shown in the table, the number of favorites variable demonstrates a significantly stronger positive correlation with anime score compared to popularity.
+The correlation for number of favorites is notably higher, indicating that favorites are a more reliable predictor of anime scores than popularity.
+Furthermore, the p-value for number of favorites suggests statistical significance, reinforcing its stronger impact on anime score.
+In contrast, popularity has a lower correlation and a higher p-value, suggesting a weaker and less significant relationship with anime score.
 
@@
 
-## First discussion point {#sec-first-point}
+## Relationship Between Popularity and Score
+The comparison of popularity and score reveals a counterintuitive situation in the dataset.
+As we analyzed, popularity (as measured by the number of users who add an anime to their list) generally reflects the visibility and widespread appeal of an anime.
+However, it does not necessarily correlate with a higher score.
+In fact, some highly popular anime with a large number of list users have relatively low scores, while other anime with higher scores have comparatively low popularity rankings.
+This suggests that, while an anime’s popularity is an important factor in its reach and visibility, it does not guarantee high ratings or audience satisfaction.
+This finding challenges the conventional assumption that popularity drives better quality ratings, and it may imply that other factors, such as niche appeal, loyal fanbases, or even specific genre preferences, play a significant role in determining anime scores.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+In future analyses, we could explore further variables that influence the relationship between popularity and ratings.
+For example, factors such as the timing of the anime’s release, genre, and the target audience could be incorporated to understand whether certain types of anime naturally achieve higher popularity without necessarily receiving better ratings.
+This would help refine our understanding of what drives anime scores beyond just the number of users who add them to their lists.
 
-## Second discussion point
+## Limitations
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+This study uses data collected from MyAnimeList (MAL), which is one of the most widely used anime databases.
+However, MAL is a single website, and the dataset is inherently limited in scope.
+The sample only reflects the opinions and ratings of a specific subset of anime viewers who are active on MAL, which may not be representative of the broader global anime-watching population.
+MAL users tend to be more engaged and passionate about anime, which could lead to a bias in the dataset.
+For example, casual viewers or those who watch anime on streaming platforms like Crunchyroll or Netflix might not be represented in this dataset.
+Therefore, the findings and conclusions drawn from this data may not fully capture the preferences of all anime fans worldwide.
 
-## Third discussion point
+Another limitation is that the dataset only captures rating scores and popularity rankings without accounting for other potentially influential factors, such as social media buzz, influencer endorsements, or broader cultural impacts that might drive anime popularity or quality perception.
+A more comprehensive dataset that includes multiple sources of ratings and reviews (e.g., streaming platforms, social media discussions, etc.) could provide a more balanced and nuanced understanding of anime rankings and their determinants.
 
-## Weaknesses and next steps
+## Conclusions
+From this analysis, we conclude that higher popularity does not necessarily mean higher scores.
+The number of list users on MAL—a proxy for popularity—does not have a strong or consistent positive correlation with the anime score.
+In contrast, the number of people who rate an anime seems to have a significant impact on its score, as those with higher ratings are often more highly scored.
+This suggests that the quality of the anime, as reflected by individual ratings, plays a much larger role in determining the overall score than the sheer volume of users adding it to their lists.
 
-Weaknesses and next steps should also be included.
+## Weaknesses and Next Steps
+The limitations of the data discussed above indicate that this analysis might not be fully generalizable to the entire anime-viewing population.
+Future research could expand the dataset to include other sources of ratings, such as those from streaming platforms or surveys of casual anime viewers.
+Additionally, considering anime genre, release timing, and platform-specific differences could provide a richer understanding of the factors influencing popularity and score.
+Incorporating these variables would help create a more comprehensive model that could explain the complexities of anime ratings beyond the simplistic measure of popularity.
+
+Future work should also focus on understanding the cultural context and how it impacts anime scores.
+For example, an anime that performs well in Japan might not necessarily have the same reception in other parts of the world.
+Exploring international audiences’ tastes and preferences could reveal interesting regional differences that are not captured by a single-site dataset like MAL.
+
+Lastly, a more detailed analysis of review sentiment (positive vs.
+negative reviews) and critical reception from multiple sources (including critics, streaming platforms, and viewers) could be beneficial.
+This would provide a more well-rounded understanding of what drives anime scores, giving us insight into the factors that most contribute to an anime’s success or failure.
 
@@
   kable()
-
 raw_data[1:5, 4:ncol(raw_data)]|>
@@
 
-$S$ = Average score for the anime/manga
-$v$ = Number users giving a score for the anime/manga †
-$m$ = Minimum number of scored users required to get a calculated score
-$C$ = The mean score across the entire Anime/Manga database
+ - $S$ = Average score for the anime/manga.
+ - $v$ = Number users giving a score for the anime/manga.
+ - $m$ = Minimum number of scored users required to get a calculated score.
+ - $C$ = The mean score across the entire Anime/Manga database.
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check.
+This compares the posterior predictions of anime score based on the popularity and number of favorites to the observed data.
+It is evident that the posterior distribution aligns well with the actual anime scores, suggesting that the model has captured the underlying data patterns effectively.
+This is a good indication that the model provides a reliable representation of how these predictors influence anime ratings.
 
 ```{r}
-#| eval: true
+#| label: fig-ppcheckandposteriorvsprior
+#| fig-cap: "Posterior predictive check for anime rating model"
+#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
 #| echo: false
@@
 #| warning: false
-#| label: fig-ppcheckandposteriorvsprior
 #| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+
+pp_check(anime_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+posterior_vs_prior(anime_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
 
@@
 ## Diagnostics
+@fig-stanareyouokay-1 is a trace plot.
+It shows the trace of the sampling process for the model parameters.
+The horizontal lines and overlapping chains suggest that the model has converged, with no signs of issues in the sampling process.
+This suggests that the posterior distribution has been adequately explored.
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+@fig-stanareyouokay-2 is an Rhat plot.
+It compares the variability within each chain to the variability between chains in the MCMC process.
+As seen in the plot, the Rhat values are all close to 1, which is an indicator that the MCMC algorithm has reached convergence.
 
 ```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
 #| label: fig-stanareyouokay
@@
 #| layout-ncol: 2
+#| echo: false
+#| warning: false
+#| message: false
+
+plot(anime_model, "trace")
+
+plot(anime_model, "rhat")
 
 ```
+
+## 90% Credibility Interval {#sec-credibility-interval}
+
+@fig-modelresults1 and @fig-modelresults2 are 90% credibility interval plots for the predictors popularity and number of favorites.
+These plots show the credible intervals for each predictor, helping to understand the uncertainty around their effects on anime score.
+
+```{r}
+#| label: fig-modelresults1
+#| fig-cap: "Credible intervals for predictors of anime score"
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+
+modelplot(anime_model, conf_level = 0.90, size = 0.2) +
+  labs(x = "90% credibility interval") +
+  theme(axis.text.y = element_text(size = 6))
+
+```
+
+```{r}
+#| label: fig-modelresults2
+#| fig-cap: "Credible intervals for predictors with x-axis limits"
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+
+model_plot <- modelplot(anime_model, conf_level = 0.90, size = 0.2)
+
+model_plot + xlim(-5, 5) +  # Adjust the limits as needed
+  labs(x = "90% Credibility Interval") +
+  theme(axis.text.y = element_text(size = 6))
+
+```
+
+## Summary
+The model diagnostics, including posterior predictive checks, trace plots, and Rhat values, suggest that the model has converged properly and is fitting the data well.
+The credible intervals for popularity and number of favorites show the uncertainty around the estimates for these predictors.
+These results provide a robust understanding of the relationship between these predictors and anime scores.
+
+# Idealized Methodology and Survey {#sec-methodology}
+
+In this section, we explore an idealized methodology for collecting data related to anime ratings and their relationship with popularity and number of favorites.
+The goal is to design a robust and comprehensive methodology that ensures reliable data collection, minimizes bias, and allows for meaningful analysis.
+The methodology would consider aspects of survey design, sampling, and the limitations of the dataset to address the research questions more effectively.
+This will provide a foundation for future research into understanding the factors that influence anime scores and their potential implications for content creators, platforms, and consumers.
+
+## Sampling Frame and Target Population
+For this study, the target population would be individuals who actively rate or review anime on MyAnimeList (MAL), as this is the source of the data in this paper.
+However, it is crucial to recognize that MAL users are not representative of the global anime-watching population.
+MAL users tend to be more engaged, active fans who have strong preferences and are more likely to rate and review anime frequently.
+Therefore, the sample would be limited to these active users, but future research could look to include a broader audience by incorporating data from other platforms (such as Crunchyroll, Funimation, or Netflix) or by conducting surveys targeting more casual anime viewers.
+
+In an ideal scenario, the sampling frame would include a stratified random sample of MAL users.
+This would help to balance the representation of different user demographics, such as age, gender, and geographic location, as well as the diversity of anime genres that users engage with.
+By ensuring that these factors are represented, the study can provide a more comprehensive understanding of the factors that contribute to anime ratings and their relationship with popularity and number of favorites.
+
+## Survey and Data Collection Methodology
+
+To supplement the data collected from MAL, we could design a survey to gather self-reported data from anime viewers.
+The survey would focus on understanding why users rate anime the way they do, exploring the relationship between anime popularity, personal preferences, and rating behavior.
+The survey would consist of a mix of quantitative and qualitative questions that explore both objective ratings (scores, popularity, etc.) and subjective impressions (favorite genres, character appeal, thematic depth, etc.).
+
+### Survey Design
+
+Quantitative Questions:
+
+1. How often do you rate anime on MyAnimeList?
+
+ - Never
+ - Occasionally
+ - Regularly
+ - Always
+
+2. What factors do you consider when rating an anime? (Select all that apply)
+
+ - Story/Plot
+ - Animation quality
+ - Characters
+ - Music/Soundtrack
+ - Themes/Philosophy
+ - Overall entertainment
+
+3. How likely are you to give a high rating (8 or above) to anime that you feel has gained high popularity?
+
+ - Very likely
+ - Likely
+ - Neutral
+ - Unlikely
+ - Very unlikely
+
+4. What is your favorite anime genre?
+
+ - Action
+ - Romance
+ - Fantasy
+ - Science Fiction
+ - Slice of Life
+ - Horror
+ - Other (please specify)
+
+5. Qualitative Questions:
+
+ - What do you think influences your decision to rate an anime higher than others? Please explain.
+
+ - Do you think anime with high popularity (many users adding it to their lists) deserve a higher score? Why or why not?
+
+ - What role does anime fan engagement (such as fan art, online discussions, etc.) play in your ratings?
+
+ - Have you ever rated an anime lower because it was overrated by others or popular on the site?
+
+This survey would be distributed through MyAnimeList or social media groups dedicated to anime discussion.
+To ensure a good response rate and data quality, we would promote the survey through anime-related channels and community groups, and incentivize participation through rewards such as anime merchandise or premium subscriptions to streaming services
+
+### Sampling Methodology
+We would adopt a stratified random sampling approach to ensure that the survey includes responses from users of different anime genres and varying levels of anime engagement.
+Users would be classified based on their interaction with the site (e.g., frequency of rating anime, diversity of genres rated) and their anime preferences (e.g., top-rated, niche anime, or specific genres).
+A stratified random sample would allow for better representation of anime enthusiasts who rate multiple genres versus those who are more focused on specific types of anime.
+
+To enhance the representativeness of the sample, the survey would be designed to collect data from users in different geographical regions, understanding the potential cultural differences that could influence the anime rating process.
+This would address one of the limitations of our MAL-only dataset, which is inherently biased toward certain cultural groups.
+
+## Data Collection and Survey Implementation
+
+The survey would be distributed primarily through MyAnimeList's messaging system or social media groups related to anime communities (e.g., Facebook, Reddit, Discord). The process would involve:
+
+1. Recruitment: Using platforms like MyAnimeList, Reddit, or Facebook to recruit participants and provide links to the survey.
+2. Informed Consent: Clear information about the purpose of the survey, ensuring participants understand how their data will be used and that it will remain anonymous.
+3. Incentives: Offering incentives such as anime-themed gift cards or subscriptions to encourage participation.
+4. Data Privacy: Ensuring privacy and confidentiality, as the survey would involve self-reported data related to individual preferences and habits.
+
+## Survey Data Analysis and Reporting
+After collecting the survey data, we would conduct both descriptive and inferential analyses.
+Descriptive statistics would summarize the frequency and distribution of responses, while inferential techniques (such as regression analysis) would help to identify relationships between anime ratings, popularity, and user preferences.
+This would complement the observational data we already have from MyAnimeList and offer deeper insights into how external factors (e.g., genre preference, fan engagement) influence anime scores.
+
+## Limitations of the Idealized Survey
+While this idealized survey methodology offers a comprehensive approach to studying anime ratings and their correlation with popularity, there are still some potential limitations:
+
+1. Self-Reported Bias: Respondents may provide socially desirable answers or overemphasize certain factors like popularity, leading to biases in the data.
+2. Sampling Bias: While we aim for a stratified random sample, anime communities on MyAnimeList and similar platforms may not fully represent the global diversity of anime viewers.
+3.
+Survey Fatigue: As surveys require participant time and effort, there’s a risk of low completion rates or non-responses from certain groups, particularly those less active on anime-related websites.
+
+## Future Directions
+In future research, it would be valuable to explore multiple sources of data from other anime platforms and crowdsourcing initiatives to broaden the scope and ensure a more representative view of global anime ratings.
+Additionally, analyzing data from real-time fan engagement (e.g., social media trends, fan art) would provide a more dynamic and holistic view of anime popularity and ratings.
+Lastly, combining observational data with survey data could offer deeper insights into the cultural and subjective factors that influence anime ratings beyond what is captured on MyAnimeList.
+
+By refining and expanding this idealized methodology, we can create more accurate models of anime ratings and uncover the hidden dynamics that shape viewers' preferences across different platforms and cultural contexts.
 

### 2024-12-04 scripts/06-model_data.R

@@ -1,25 +1,29 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Model the relationship between anime scores, popularity, and number of favorites
+# Author: Doran Wang
+# Date: 30 November 2024
+# Contact: doran.wang@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Pre-requisites: 
+  # - Access the 03-clean_data.R first
+  # - The `tidyverse` package must be installed and loaded
+  # - The `arrow` package must be installed and loaded
+  # - The `rstanarm` package must be installed and loaded
+# Any other information needed? [Update if necessary]
 
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(arrow)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+cleaned_data <- read_parquet("data/02-analysis_data/cleaned_data.parquet")
 
 ### Model data ####
-first_model <-
+anime_model <-
   stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
+    formula = score ~ popularity + num_favorites,
+    data = cleaned_data,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
@@ -27,11 +31,8 @@ first_model <-
     seed = 853
   )
 
-
 #### Save model ####
 saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+  anime_model,
+  file = "models/anime_model.rds"
 )
-
-

### 2024-12-04 paper/paper.qmd
Update paper pdf

@@
 These data points were then cleaned and processed for analysis using the statistical programming software R [@citeR].
-The analysis utilized several R packages from the tidyverse [@citeTidyverse], ggplot2 [@citeGgplot] for visualization, `rstanarm` [@rstanarm], `arrow` [@citearrow] and `knitr` [@citeKnitr]`.
+The analysis utilized several R packages from the tidyverse [@citeTidyverse], ggplot2 [@citeGgplot2] for visualization, `rstanarm` [@rstanarm], `arrow` [@citearrow] and `knitr` [@citeKnitr]`.
 Data processing tasks, such as handling missing values and transforming variables, were carried out to ensure the dataset was ready for analysis.
@@
 ```{r}
-#| label: fig-favorites-histogram
+#| label: fig-popularity-histogram
 #| fig-cap: "Histogram of Popularity for Top 10 Highest-Rated Anime"
